\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}
\usepackage[margin=1.4cm]{geometry}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.15in}
 \addtolength{\textwidth}{0.3in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{0pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[3]{
    \item
    \begin{tabular*}{1.001\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2} \\
      \textit{\small #3}
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}\vspace{0pt}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

%----------HEADING----------
\begin{center}
    {\Large \scshape David Londoño} \\[2mm]
    \vspace{-1pt}
    \footnotesize \raisebox{-0.1\height}
    \faPhone\ \underline{+57 317 2939347} ~
    {\faEnvelope\  \underline{dlondon.dev@gmail.com}} ~
    {\faLinkedin\ \underline{\href{https://www.linkedin.com/in/davidldv/}{linkedin.com/in/davidldv}}  ~
    {\faGithub\ \underline{\href{https://github.com/davidldv}{github.com/davidldv}} ~
    {\faBriefcase\ \underline{\href{https://dlondon.tech/}{dlondon.tech/}}
    \vspace{-4pt}
\end{center}
%---------PROFESSIONAL DESC--------
\vspace{4pt}
\small{
Software Engineer with full-stack production experience in \textbf{TypeScript, Next.js, and PostgreSQL}, focused on \textbf{Application Security} and secure software design. Experienced in implementing authentication and authorization systems (\textbf{OAuth, RBAC, session management}), input validation, and auditability in production environments.
Application of \textbf{OWASP} Top 10 principles, \textbf{threat modeling}, and \textbf{offensive testing practices} to identify and mitigate real-world vulnerabilities. Actively developing security-focused projects and validating systems through hands-on exploitation and defense.
Open to visa sponsorship (Germany / EU Blue Card, US). Languages: English C1, Spanish native, German B1.
}
\vspace{-8pt}
%-----------Experience---------------
\section{Work Experience}
\vspace{-1pt}
    \resumeSubHeadingListStart
    \resumeSubheading{Materiales La Bodega}{Mar 2026 -- Present}{Full Stack Engineer}{Remote}
            \resumeItemListStart
                \resumeItem{Own and scale a production retail platform for a hardware business, processing \textasciitilde{}\$1.5M COP/day across e-commerce and in-store operations; responsible for authentication, session security, and role-based access for staff vs. customer surfaces.}
                \resumeItem{Hardened the application layer against common web risks (\textbf{OWASP Top 10}): parameterized queries, server-side input validation, \textbf{CSRF} protection on state-changing endpoints, and least-privilege database roles.}
            \resumeItemListEnd
        \resumeSubheading{Tambora}{Jul 2025 -- Sep 2025}{Frontend Developer}{Remote}
            \resumeItemListStart
                \resumeItem{Migrated business-critical legacy modules from \textbf{jQuery} to \textbf{React}, achieving a 40\% bundle-size reduction and shrinking the client-side attack surface by consolidating logic into a modular, \textbf{Atomic Design} component library.}
                \resumeItem{Engineered \textbf{CI/CD pipelines} on \textbf{Azure} to replace manual SSH-based deploys, cutting deployment time from 2+ hours to under 15 minutes and enabling automated test gates — the foundation for adding \textbf{SAST/dependency-scan} steps in the pipeline.}
            \resumeItemListEnd
    \resumeSubHeadingListEnd
    \vspace{-16pt}
%-----------PROJECTS-----------
\section{Projects}
    \vspace{-2pt}
    \resumeSubHeadingListStart
 \resumeProjectHeading
            {\textbf{{PairCode}} $|$ \emph{\href{https://paircode-lime.vercel.app/}{Website}{ $|$ }\href{https://github.com/davidldv/paircode}{Source Code}}}{Next.js $|$ PostgreSQL $|$ WebSockets}{Secure collaborative system with verified identity, and hardened communication layer.}
            \\[5mm]
          \resumeItemListStart
            \resumeItem{Built an in-house auth stack: \textbf{EdDSA JWTs}, rotating \textbf{refresh tokens} with reuse detection, \textbf{Argon2id hashing}, and \textbf{CSRF} protection.}
            \resumeItem{Designed a custom \textbf{WebSocket} server with single-use ticket handshake, per-event authorization, and \textbf{RBAC enforced} server-side.}
            \resumeItem{Implemented the realtime room layer: presence, typing, shared \textbf{threaded context}, and persistent history that survives reconnects.}
          \resumeItemListEnd
 \vspace{-4pt}
% -------------------------------------------------------------------
% TODO (David): Add 1-2 SECURITY-FOCUSED projects here before applying.
% Good options, pick what you actually build:
%   - OWASP Top 10 lab (vulnerable app + writeups of exploit + fix)
%   - JWT pitfalls demo (alg=none, weak secret, kid injection)
%   - SSRF / SSRF-to-metadata-service lab on a cloud VM
%   - Custom Semgrep / CodeQL rule for a class of bug
%   - Dockerized app hardening project (distroless, non-root, seccomp)
%   - CTF writeup repo (HackTheBox / TryHackMe / picoCTF)
% Example skeleton:
% \resumeProjectHeading
%   {\textbf{SecLab-JWT} $|$ \emph{\href{URL}{Source Code}}}{Python $|$ Docker}{Lab demonstrating JWT misconfigurations and defenses.}
%   \resumeItemListStart
%     \resumeItem{Reproduced alg=none, key-confusion (RS256->HS256), and weak-secret brute-force attacks against a Flask API.}
%     \resumeItem{Wrote defensive middleware with strict algorithm allow-list, key rotation, and audience/issuer checks; documented findings as a short write-up.}
%   \resumeItemListEnd
% -------------------------------------------------------------------
\resumeSubHeadingListEnd
\vspace{-14pt}

 %-----------EDUCATION-----------
\section{Education \& Training} \\[1mm]
\vspace{-2pt}
    \resumeSubHeadingListStart
    \resumeSubheading
      {EliteStack Bootcamp}{Jun 2024 -- Jul 2024}
      {Full-Stack Development}{Pereira, Colombia}
  \resumeSubHeadingListEnd
    \resumeItemListStart
        \resumeItem {Linux/CLI, TypeScript, Node.js, Docker, REST APIs, WebSockets, Next.js, AWS.}
        \resumeItem {Self-directed continuing study: Operating Systems, Computer Architecture, Networking, Algorithms \& Data Structures, Applied Machine Learning. Two years of university-level coursework in Systems \& Computing Engineering (Universidad Tecnológica de Pereira, not completed).}
    \resumeItemListEnd
\vspace{-12pt}
 %-----------CERTIFICATIONS-----------
\section{Certifications \& Security Training}
\vspace{-2pt}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
% TODO (David): Replace with your real entries. Even "In progress" is worth listing
% once you've paid/enrolled. Suggested ordering of effort vs. payoff:
%   1. CompTIA Security+ (recruiter-readable baseline, ~2-3 months study)
%   2. TryHackMe SOC Level 1 / Pre-Security path (free, shows activity)
%   3. INE eJPT (practical offensive entry cert)
%   4. PortSwigger Web Security Academy (free, strong AppSec signal)
%   5. Longer term: Burp Suite Certified Practitioner (BSCP) or OSCP
     \textbf{In progress}{: CompTIA Security+ (target: 2026-Q3), PortSwigger Web Security Academy.} \\[1mm]
     \textbf{Platforms}{: HackTheBox — @davidldv, TryHackMe — dlondon.dev.} \\[1mm]
    }}
 \end{itemize}
 \vspace{-14pt}

  %-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
\vspace{-2pt}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: TypeScript, JavaScript, Python, C, SQL, Bash, HTML/CSS.} \\[1mm]
     \textbf{Security}{: OWASP Top 10, OAuth 2.0 / OIDC, JWT, RBAC, input validation, secure session \& cookie handling, CSRF/XSS/SQLi defenses, secrets management, threat modeling (STRIDE), secure code review.} \\[1mm]
     \textbf{Tooling}{: Burp Suite, nmap, Wireshark, Semgrep, Trivy, Docker, Git, Postman, Linux, Jira.} % TODO: keep only tools you actually use
     \\[1mm]
     \textbf{Cloud \& DevOps}{: AWS, Azure, CI/CD (Azure Pipelines), containerization, Linux hardening basics.} \\[1mm]
     \textbf{Frameworks \& Data}{: Next.js, React, Node.js, Prisma, PostgreSQL, MongoDB, REST APIs, WebSockets, Jest, Zod, Tailwind CSS.} \\[1mm]
    }}
 \end{itemize}
 \vspace{-16pt}

 %-----------LANGUAGES-----------
\section{Languages}
\vspace{-2pt}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Spanish}: Native \quad\textbar\quad \textbf{English}: C1 (Advanced) \quad\textbar\quad \textbf{German}: B1.
    }}
 \end{itemize}
 \vspace{-10pt}

\end{document}
